A Case Study in Preserving a High Energy Physics Application

### 2014-01-16 paper.tex
Removed junk at top.
Reworked the first page.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

@@

\title{A Case Study in Preserving a High Energy Physics Application}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{6} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Haiyan Meng\\
    \affaddr{Department of Computer Science and Engineering}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{hmeng@nd.edu}
% 2nd. author
\alignauthor
Matthias Wolf\\
    \affaddr{Department of Physics}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{mwolf3@nd.edu}
% 3rd. author
\alignauthor
Anna Woodard\\
    \affaddr{Department of Physics}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{awoodard@nd.edu}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor 
Peter Ivie\\
    \affaddr{Department of Computer Science and Engineering}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{pivie@nd.edu}
% 5th. author
\alignauthor 
Michael Hildreth\\
    \affaddr{Department of Physics}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{Michael.D.Hildreth.2@nd.edu}
% 6th. author
\alignauthor 
Douglas Thain\\
    \affaddr{Department of Computer Science and Engineering}\\
    \affaddr{University of Notre Dame}\\
    \affaddr{Notre Dame, Indiana}\\
    \email{dthain@nd.edu}
}
\date{15 January 2014}
\maketitle
\begin{abstract}
...
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
...
\section{Introduction of the exmaple}
\subsection{Background}
Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.

>>>>

@@

\title{A Case Study in Preserving a High Energy Physics Application}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|awoodard|pivie|mhildreth|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

\begin{abstract}
...
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

\section{Introduction}

Reproducibility is a cornerstone of the scientific process.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

The overall reproduction of a computation has three broad components,
each of which suggests somewhat different approaches:

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system).
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use.  This approach has
been used to some success with systems X, Y, and Z.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

However, this simple approach is not sufficient for large applications
that are run in complex social environments.

\begin{itemize}
\item There may be {\bf implicit dependencies} on items that are
not apparent to the end user.  For example, they may understand that
they rely on a particular data analysis package, but would have
no reason to know that the package has further dependencies on
other libraries and configuration files.  Or, they may know that
the computation only runs correctly on a particular machine, but
not know this is because it relies on data in a filesystem that
is mounted only on that machine.

\item The {\bf granularity} of the dependencies may not be well understood.
For example, the user may understand that a computation depends upon
a data collection that is 1TB in overall size, but not have detailed
knowledge that it only requires three files totalling 300MB out of that
whole collection

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository, or a scalable filesystem.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

\item Where {\bf common dependencies} are widely used, it may be ineffecient or
impossible to store one copy of each dependency for each archived object.
Some form of sharing or de-duplication is necessary in order to keep
the archive to a reasonable size.
\end{itemize}

In this paper, we demonstrate many of these difficulties by presenting
a case study of a high energy physics application, considered from
the perspective of preservation.  The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
Then, we develop three techniques for observing and capturing the
dependencies associated with the system, comparing the cost of capture,
the size of the preserved object, and the flexibility of the resulting
object.  We conclude with some reflections on the challenges of preservation
and advice for future efforts.

\section{Introduction of the exmaple}
\subsection{Background}
Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
